---
title: "Deploy the app"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{deploy-the-app}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(exploratorium)
```

```{r parsermd-chunk-1, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  echo = TRUE
)
```

*The aim of this article is to explain you how to deploy the app on shinyapps.io.*

The application is continuously deployed on the prevention.shinyapps.io account belonging to
PSCH.

* The `main` branch can be found at https://prevention.shinyapps.io/exploratorium-dev/
* The `production` branch on https://prevention.shinyapps.io/exploratorium/


### Environment variables

Two environment variables have to be defined in`.gitlab-ci.yml` or in `~/.Renviron` for a manual deployment:

* `SHINYAPPS_IO_TOKEN`
* `SHINYAPPS_IO_SECRET` 

Values can be found at https://www.shinyapps.io/admin/#/tokens.
You will then need to click on `Show` to see the two variables.


### Manual deployment

To deploy the app manually, you can directly use the script `dev/deploy_app.R` in your development environment.


```{r parsermd-chunk-2}
rstudioapi::navigateToFile("dev/deploy_app.R")
```

